material and methods

### 2017-08-22 man/ms_1_material_methods.Rmd
update resilience notes

To evaluate the effects of the drought events on greeennes and tree growth we used the four different resilience metrics [@Lloret2011]

>>>>

To evaluate the effects of the disturbance events on greeennes and tree growth we used four resilience indices proposed by @Lloret2011: resilience (*Rs*), resistance, recovery (*Rc*) and relative resilience (*RRs*). We computed the values of these indices for tree growth and greenness during each drought event. We considered 2005 and 2012 as a single drought event.

The resistance index (*Rt*) quantifies the severity of the impact of the disturbance in the year it occurred. It is estimated as the ratio between the performance during and befor the disturbance:

Resistance (*Rt*) = Drought / Predrought

The Recovery index (*Rc*) is the ability to recover relative to the damage experienced during disturbance, and it is estimated as the ratio between performance after and during disturbance:

Recovery (*Rc*) = Postdrought / Drought

The Resilience index (*Rs*) is the capacity to reach pre-disturbance performance levels, and it is estimated as the ratio between the performance after and before disturbance: Resilience (*Rs*)

Re

The indices For each target variable (tree growth and greenness) the indices evaluate
